---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# research-compendium

<!-- badges: start -->
<!-- badges: end -->

The goal of research-compendium is to host a tutorial on "Improve your code for Epidemic Analysis with R".

## Usage

Visualize this content as a webpage at <https://epiverse-trace.github.io/research-compendium/>

## Contributing

Contributions are always welcome!

See our [Contributing guide](CONTRIBUTING.md) for ways to get started.

Please adhere to this project's [Code of Conduct](CODE_OF_CONDUCT.md).

<!-- ## Support -->

<!-- Please see our [Getting help guide](/.github/SUPPORT.md) for support. -->

## Authors

- [@avallecam](https://github.com/avallecam/)
- [@CarmenTamayo](https://github.com/CarmenTamayo)
- [@jamesmbaazam](https://github.com/jamesmbaazam/)

```{r,echo=FALSE}
readCitationFile(file = "inst/CITATION")
```


## License

Read the [License](LICENSE.md) of this lesson.


